Using a linear Taylor series approximation to estimate rounding error

### 2024-07-07 text/23/exponential-hedging-hyperprior.Rmd
Updated 2024 Rmd files

---
title: "The hedging hyperprior for the exponential distribution"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

@@

```{r}
x_max <- 3

@@

post05 <- 1/qgamma(c(0.975), a1, b1) 
post95 <- 1/qgamma(c(0.025), a1, b1)

```

@@

```{r}
g_grid <- g(x_grid, a0, b0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
f_grid <- f(xbar, x_grid)^n
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
h_grid <- g(x_grid, a1, b1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r}
density <- outer(theta_grid, lambda_grid, gstar)
# density[12:32, ] <- NA
# density[11:40, ] <- NA
density[density>0.3] <- 0.3
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  theta_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="theta",
  ylab="lambda",
  theta = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  theta_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(10, 25, 50, 75, 90)/100,
  xlab="theta",
  ylab="lambda")
```

>>>>

---
title: "The hedging hyperprior for the exponential distribution"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r exponential-hedging-hyperprior-01}
x_max <- 3

@@

post05 <- 1/qgamma(c(0.975), a1, b1) 
post95 <- 1/qgamma(c(0.025), a1, b1) 
```

@@

```{r exponential-hedging-hyperprior-02}
g_grid <- g(x_grid, a0, b0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r exponential-hedging-hyperprior-03}
f_grid <- f(xbar, x_grid)^n
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r exponential-hedging-hyperprior-04}
h_grid <- g(x_grid, a1, b1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r exponential-hedging-hyperprior-05}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r exponential-hedging-hyperprior-06}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r exponential-hedging-hyperprior-07}
density <- outer(theta_grid, lambda_grid, gstar)
# density[12:32, ] <- NA
# density[11:40, ] <- NA
density[density>0.3] <- 0.3
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  theta_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="theta",
  ylab="lambda",
  theta = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r exponential-hedging-hyperprior-08}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r exponential-hedging-hyperprior-09}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r exponential-hedging-hyperprior-10}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  theta_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(10, 25, 50, 75, 90)/100,
  xlab="theta",
  ylab="lambda")
```

### 2024-07-07 text/23/mcnemar-test.Rmd
Updated 2024 Rmd files

---
title: "McNemar's test"
source: "New"
author: Steve Simon
date: 2023-10-31
categories:
- Blog post
tags:
- Measuring benefit and risk
output: html_document
---

@@

```{r}
a <- 833; b <- 125; c <- 2; d <- 160
n <- a + b + c + d
r1 <- round(100*(a+b)/n)
c1 <- round(100*(a+c)/n)
T <- round((b-c)^2/(b+c), 1)
```

@@

```{r}
mcnemar.test(matrix(c(833, 125, 2, 160), nrow=2), correct=FALSE)
```

>>>>

---
title: "McNemar's test"
source: "New"
author: Steve Simon
date: 2023-10-31
categories:
- Blog post
tags:
- Measuring benefit and risk
- Rmarkdown code
output: html_document
page_update: complete
---

@@

```{r mcnemar-test-01}
a <- 833; b <- 125; c <- 2; d <- 160
n <- a + b + c + d
r1 <- round(100*(a+b)/n)
c1 <- round(100*(a+c)/n)
T <- round((b-c)^2/(b+c), 1)
```

@@

```{r mcnemar-test-02}
mcnemar.test(matrix(c(833, 125, 2, 160), nrow=2), correct=FALSE)
```

### 2024-07-07 text/23/modified-power-prior.Rmd
Updated 2024 Rmd files

---
title: "The modified power prior"
source: "New"
date: "2023-03-04"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

```{r setup}
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

>>>>

---
title: "The modified power prior"
source: "New"
date: "2023-03-04"
categories:
- Blog post
tags:
- Bayesian statistics
- Incomplete pages
output: html_document
page_update: complete
---

```{r modified-power-prior-01}
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

### 2024-07-07 text/23/non-standard-evaluation.Rmd
Updated 2024 Rmd files

---
title: "Non-standard evaluation inside functions and loops"
source: "New"
date: "2023-04-04"
categories:
- Blog post
tags:
- R software
output: html_document
---

@@

```{r}
old_data <- data.frame(
  w=0:3,
  x=1:4,
  y=2:5,
  z=3:6)
new_data <- old_data[ , c("w", "x")]
new_data
```

@@

```{r}
new_data <- select(old_data, w, x)
new_data
```

@@

```{r}
new_data <- old_data[old_data$w < 2, ]
new_data
```

@@

```{r}
new_data <- filter(old_data, w < 2)
new_data
```

@@

```{r}
for (v in c("w", "x")) {
  print(table(old_data[ , v]))
}
```

@@

```{r, error=TRUE}
for (v in c("w", "x")) {
  count(old_data, v)
}
```

@@

```{r, error=TRUE}
for (v in c("w", "x")) {
  print(count(old_data, .data[[v]]))
}
```

@@

```{r}
reduce <- function(old_data, variable_name) {
  old_data[ , variable_name]
}
reduce(old_data, "w")
```

@@

```{r, error=TRUE}
reduce <- function(old_data, variable_name) {
  select(old_data, variable_name)
}
reduce(old_data, w)
```

@@

```{r, error=TRUE}
reduce(old_data, "w")
```

@@

```{r, error=TRUE}
reduce <- function(old_data, variable_name) {
  select(old_data, {{variable_name}})
}
reduce(old_data, w)
```

@@

```{r, error=TRUE}
reduce <- function(old_data, ...) {
  select(old_data, ...)
}
reduce(old_data, w, x)
```

@@

```{r, error=TRUE}
reduce <- function(old_data, variable_string) {
  select(old_data, .data[[variable_string]])
}
reduce(old_data, "w")
```

@@

```{r, error=TRUE}
reduce <- function(old_data, variable_string) {
  select(old_data, .data[[variable_string]])
}
reduce(old_data, c("w", "x"))
```

@@

```{r, error=TRUE}
reduce <- function(old_data, variable_string) {
  select(old_data, any_of(variable_string))
}
reduce(old_data, c("w", "x"))
```

>>>>

---
title: "Non-standard evaluation inside functions and loops"
source: "New"
date: "2023-04-04"
categories:
- Blog post
tags:
- R software
- Rmarkdown code
output: html_document
page_update: complete
---

@@

```{r non-standard-evaluation-01}
old_data <- data.frame(
  w=0:3,
  x=1:4,
  y=2:5,
  z=3:6)
new_data <- old_data[ , c("w", "x")]
new_data
```

@@

```{r non-standard-evaluation-02}
new_data <- select(old_data, w, x)
new_data
```

@@

```{r non-standard-evaluation-03}
new_data <- old_data[old_data$w < 2, ]
new_data
```

@@

```{r non-standard-evaluation-04}
new_data <- filter(old_data, w < 2)
new_data
```

@@

```{r non-standard-evaluation-05}
for (v in c("w", "x")) {
  print(table(old_data[ , v]))
}
```

@@

```{r non-standard-evaluation-06, error=TRUE}
for (v in c("w", "x")) {
  count(old_data, v)
}
```

@@

```{r non-standard-evaluation-07, error=TRUE}
for (v in c("w", "x")) {
  print(count(old_data, .data[[v]]))
}
```

@@

```{r non-standard-evaluation-08}
reduce <- function(old_data, variable_name) {
  old_data[ , variable_name]
}
reduce(old_data, "w")
```

@@

```{r non-standard-evaluation-09, error=TRUE}
reduce <- function(old_data, variable_name) {
  select(old_data, variable_name)
}
reduce(old_data, w)
```

@@

```{r non-standard-evaluation-10, error=TRUE}
reduce(old_data, "w")
```

@@

```{r non-standard-evaluation-11, error=TRUE}
reduce <- function(old_data, variable_name) {
  select(old_data, {{variable_name}})
}
reduce(old_data, w)
```

@@

```{r non-standard-evaluation-12, error=TRUE}
reduce <- function(old_data, ...) {
  select(old_data, ...)
}
reduce(old_data, w, x)
```

@@

```{r non-standard-evaluation-13, error=TRUE}
reduce <- function(old_data, variable_string) {
  select(old_data, .data[[variable_string]])
}
reduce(old_data, "w")
```

@@

```{r non-standard-evaluation-14, error=TRUE}
reduce <- function(old_data, variable_string) {
  select(old_data, .data[[variable_string]])
}
reduce(old_data, c("w", "x"))
```

@@

```{r non-standard-evaluation-15, error=TRUE}
reduce <- function(old_data, variable_string) {
  select(old_data, any_of(variable_string))
}
reduce(old_data, c("w", "x"))
```

### 2024-07-07 text/23/normal-hedging-hyperprior-part-1.Rmd
Updated 2024 Rmd files

---
title: "The hedging hyperprior for the normal distribution: unknown mean, known precision"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---

```{r setup}
suppressMessages(suppressWarnings(library(MASS)))
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

@@

```{r}
x_max <- 8

@@

```{r}
g_grid <- g(x_grid, mu0, tau0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
f_grid <- f(xbar, x_grid, tauF)^n
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) + 
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
h_grid <- g(x_grid, mu1, tau1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r}
density <- outer(mu_grid, lambda_grid, gstar)
density[16:44, ] <- NA
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  mu_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="mu",
  ylab="lambda",
  mu = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  mu_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(50, 75, 90)/100,
  xlab="mu",
  ylab="lambda")
```

>>>>

---
title: "The hedging hyperprior for the normal distribution: unknown mean, known precision"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
- Rmarkdown graphs
output: html_document
page_update: complete
---

```{r normal-hedging-prior-01}
suppressMessages(suppressWarnings(library(MASS)))
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

@@

```{r normal-hedging-prior-02}
x_max <- 8

@@

```{r normal-hedging-prior-03}
g_grid <- g(x_grid, mu0, tau0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-04}
f_grid <- f(xbar, x_grid, tauF)^n
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) + 
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-05}
h_grid <- g(x_grid, mu1, tau1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-06}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r normal-hedging-prior-07}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-08}
density <- outer(mu_grid, lambda_grid, gstar)
density[16:44, ] <- NA
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  mu_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="mu",
  ylab="lambda",
  mu = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r normal-hedging-prior-09}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-10}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-11}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  mu_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(50, 75, 90)/100,
  xlab="mu",
  ylab="lambda")
```

### 2024-07-07 text/23/normal-hedging-hyperprior-part-2.Rmd
Updated 2024 Rmd files

---
title: "The hedging hyperprior for the normal distribution: known mean, unknown precision"
source: "New"
date: "2023-03-14"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---

```{r setup}
suppressMessages(suppressWarnings(library(MASS)))
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

@@

```{r}
x_max <- 8

@@

```{r}
g_grid <- g(x_grid, alpha0, beta0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
f_grid <- rep(NA, length(x_grid))
for (i in 1:length(x_grid)) {
  f_grid[i] <- prod(f(x, muF, x_grid[i]))
}
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) + 
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
h_grid <- g(x_grid, alpha1, beta1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r}
lambda_grid <- seq(0, 1, length=60)
tau_grid <- seq(0, x_max, length=60)

@@

```{r, eval=FALSE}
density <- outer(tau_grid, lambda_grid, gstar)
density[16:44, ] <- NA
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  mu_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="tau",
  ylab="lambda",
  theta = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
tau_grid <- seq(0, x_max, length=60)

@@

```{r, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r, eval=FALSE}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  mu_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(50, 75, 90)/100,
  xlab="tau",
  ylab="lambda")
```

>>>>

---
title: "The hedging hyperprior for the normal distribution: known mean, unknown precision"
source: "New"
date: "2023-03-14"
categories:
- Blog post
tags:
- Bayesian statistics
- Rmarkdown graphs
output: html_document
page_update: complete
---

```{r normal-hedging-prior-20}
suppressMessages(suppressWarnings(library(MASS)))
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

@@

```{r normal-hedging-prior-21}
x_max <- 8

@@

```{r normal-hedging-prior-22}
g_grid <- g(x_grid, alpha0, beta0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-23}
f_grid <- rep(NA, length(x_grid))
for (i in 1:length(x_grid)) {
  f_grid[i] <- prod(f(x, muF, x_grid[i]))
}
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) + 
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-24}
h_grid <- g(x_grid, alpha1, beta1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-25}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r normal-hedging-prior-26}
lambda_grid <- seq(0, 1, length=60)
tau_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-27, eval=FALSE}
density <- outer(tau_grid, lambda_grid, gstar)
density[16:44, ] <- NA
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  mu_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="tau",
  ylab="lambda",
  theta = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r normal-hedging-prior-28, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
tau_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-29, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-30, eval=FALSE}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  mu_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(50, 75, 90)/100,
  xlab="tau",
  ylab="lambda")
```

### 2024-07-07 text/23/normal-hedging-hyperprior-part-3.Rmd
Updated 2024 Rmd files

---
title: "The hedging hyperprior for the normal distribution: unknown mean, unknown precision"
source: "New"
date: "2023-03-21"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---

```{r setup}
suppressMessages(suppressWarnings(library(MASS)))
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

@@

```{r}
x_max <- 8

@@

```{r}
g_grid <- g(x_grid, alpha0, beta0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
f_grid <- rep(NA, length(x_grid))
for (i in 1:length(x_grid)) {
  f_grid[i] <- prod(f(x, muF, x_grid[i]))
}
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) + 
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
h_grid <- g(x_grid, alpha1, beta1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r, eval=FALSE}
density <- outer(theta_grid, lambda_grid, gstar)
density[16:44, ] <- NA
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  mu_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="theta",
  ylab="lambda",
  theta = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r, eval=FALSE}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  mu_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(50, 75, 90)/100,
  xlab="theta",
  ylab="lambda")
```

>>>>

---
title: "The hedging hyperprior for the normal distribution: unknown mean, unknown precision"
source: "New"
date: "2023-03-21"
categories:
- Blog post
tags:
- Bayesian statistics
- Rmarkdown graphs
output: html_document
page_update: complete
---

```{r normal-hedging-prior-40}
suppressMessages(suppressWarnings(library(MASS)))
suppressMessages(suppressWarnings(library(tidyverse)))
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=2)
```

@@

```{r normal-hedging-prior-41}
x_max <- 8

@@

```{r normal-hedging-prior-42}
g_grid <- g(x_grid, alpha0, beta0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-43}
f_grid <- rep(NA, length(x_grid))
for (i in 1:length(x_grid)) {
  f_grid[i] <- prod(f(x, muF, x_grid[i]))
}
x_color <- "white"
data.frame(x=x_grid, y=f_grid) %>%
  ggplot(aes(x, y)) + 
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-44}
h_grid <- g(x_grid, alpha1, beta1)
outside <- x_grid < post05 | x_grid > post95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=h_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x_grid, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

@@

```{r normal-hedging-prior-45}
knitr::opts_chunk$set(echo=TRUE, fig.width=8, fig.height=8)
```

```{r normal-hedging-prior-46}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-47, eval=FALSE}
density <- outer(theta_grid, lambda_grid, gstar)
density[16:44, ] <- NA
op <- par(bg = "white")
z_max <- max(density, na.rm=TRUE)
persp(
  mu_grid, 
  lambda_grid, 
  density, 
  zlim=c(0, 1.1*z_max),
  xlab="theta",
  ylab="lambda",
  theta = 135, 
  phi = 30, 
  expand=0.5,
  ticktype="detailed")
```

@@

```{r normal-hedging-prior-48, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
theta_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-49, eval=FALSE}
lambda_grid <- seq(0, 1, length=60)
mu_grid <- seq(0, x_max, length=60)

@@

```{r normal-hedging-prior-50, eval=FALSE}
density <- density / sum(density, na.rm=TRUE)
density %>%
  as.vector %>%
  sort %>%
  rev -> sorted_density
cumulative_p <- 0
for (p in sorted_density) {
  cumulative_p <- p + cumulative_p
  density[density==p] <- cumulative_p
}
contour(
  mu_grid, 
  lambda_grid, 
  density,
  labcex=1,
  levels=c(50, 75, 90)/100,
  xlab="theta",
  ylab="lambda")
```

### 2024-07-07 text/23/taylor-series-approximation.Rmd
Updated 2024 Rmd files

---
title: "Using a linear Taylor series approximation to estimate rounding error"
source: "New"
author: Steve Simon
date: 2023-09-02
categories:
- Blog post
tags:
- Mathematics
output: html_document
---

@@

```{r, echo=FALSE}
d0 <- 2.5
t0 <- 20
pace0 <- t0 / d0
d1 <- d0 - 0.05
d2 <- d0 + 0.05
pace1 <- round(t0 / d1, 4)
pace2 <- round(t0 / d2, 4)
approx1 <- round(t0/d0-(d1-d0)*t0/(d0^2), 4)
approx2 <- round(t0/d0-(d2-d0)*t0/(d0^2), 4)
```

@@

```{r, echo=FALSE}
library(ggplot2, quiet=TRUE)
d <- seq(d0-1, d0+1, length=501)
pace <- t0/d
truth <- data.frame(d, t0/d)
approx <- data.frame(d, pace=t0/d0 - (d-d0)*t0/d0^2)

@@

```{r, echo=FALSE}
library(ggplot2, quiet=TRUE)
d <- seq(d0-0.1, d0+0.1, length=501)
pace <- t0/d
truth <- data.frame(d, t0/d)
approx <- data.frame(d, pace=t0/d0 - (d-d0)*t0/d0^2)

>>>>

---
title: "Using a linear Taylor series approximation to estimate rounding error"
source: "New"
author: Steve Simon
date: 2023-09-02
categories:
- Blog post
tags:
- Mathematics
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r taylor-series-approximation-01, echo=FALSE}
d0 <- 2.5
t0 <- 20
pace0 <- t0 / d0
d1 <- d0 - 0.05
d2 <- d0 + 0.05
pace1 <- round(t0 / d1, 4)
pace2 <- round(t0 / d2, 4)
approx1 <- round(t0/d0-(d1-d0)*t0/(d0^2), 4)
approx2 <- round(t0/d0-(d2-d0)*t0/(d0^2), 4)
```

@@

```{r taylor-series-approximation-02, echo=FALSE}
library(ggplot2, quiet=TRUE)
d <- seq(d0-1, d0+1, length=501)
pace <- t0/d
truth <- data.frame(d, t0/d)
approx <- data.frame(d, pace=t0/d0 - (d-d0)*t0/d0^2)

@@

```{r taylor-series-approximation-03, echo=FALSE}
library(ggplot2, quiet=TRUE)
d <- seq(d0-0.1, d0+0.1, length=501)
pace <- t0/d
truth <- data.frame(d, t0/d)
approx <- data.frame(d, pace=t0/d0 - (d-d0)*t0/d0^2)
